\begin{rubric}{Professional Experience}
    \entry*[02.2025 -- Present] \textbf{Researcher -- ZIPD, University of Trier, Germany}

    	\textbullet~Led the design and development of a \textbf{Retrieval-Augmented Generation} (RAG) system with a user-friendly interface to summarize scientific texts for non-expert users.\par

    	\textbullet~Defined a 37-point evaluation framework and collaborated across a multidisciplinary team.\par\par

    \entry*[04.2022 -- 01.2025] \textbf{Doctoral Researcher -- University of Stuttgart \& University of Bamberg, Germany}

    	\textbullet~Researched \textbf{Conditional text generation} by using psychological emotion theories to guide \textbf{LLMs} outputs to improve their emotional intelligence and adaptability.\par

    	\textbullet~Investigated \textbf{Multi-Objective Prompt Optimization} methods for \textbf{LLMs}.\par

    	\textbullet~Conducted research prompt optimization methods for language models, incorporating \textbf{Reinforcement Learning} approaches.\par

    	\textbullet~Mentored and supervised bachelor’s and master’s students in NLP courses and thesis.\par

    \entry*[06.2018 -- 09.2021] \textbf{Data Scientist -- Kantar, México}

    	\textbullet~Coordinated with commercial teams to align ML solutions with client needs, enhancing brand strategy and market impact.\par
%
    	\textbullet~Built TextAI’s engine a multilingual NLP system for \textbf{NER}, \textbf{Sentiment Analysis}, \textbf{Machine Translation} and \textbf{Topic Modeling}, then \textbf{led a team} to scale TextAI to 10+ languages.\par

    	\textbullet~Developed \textbf{Machine Translation} models to convert specialized language (e.g., legal, medical) into user-friendly language for specific audiences.

    	\textbullet~Developed a \textbf{recommender system} to analyze purchase behavior, suggest relevant products, recommend substitutes, and organize items into categories.\par

    	\textbullet~Developed \textbf{Model distillation} and \textbf{Quantization Techniques} to optimize inference performance and reduce cloud deployment costs.

%
% Blank lines result in extra space!
%
    \entry*[02.2017 -- 08.2017] \textbf{Research Intern -- University of Wolverhampton, UK}

    \textbullet~Developed a Machine Learning \textbf{Sentiment Analysis} application for Spanish texts.
%
\end{rubric}